---
title: "My first Quarto Page"
format: html
---
# Exercise 1
I will explore this data set and prepare the environment
Practice makes perfect

```{r}
library(tidyverse) 
```

```{r}
getwd()
list.files()
```

```{r}

library(tidyverse)
if (!file.exists("video_view.csv")) {
data_url <- paste0(
"https://raw.githubusercontent.com/hannesdatta/",
"course-dprep/refs/heads/main/material/tutorials/r-bootcamp-rev/",
"video_view.csv"
)
download.file(data_url, "video_view.csv")
}
videos <- read_csv("video_view.csv")
```

```{r}
head(videos)
names(videos)
glimpse(videos)
summary(videos$watch_rate)
```

# Example 1
What each line does:
• videos %>% starts from the full table
• select(...) keeps only 5 relevant variables
• filter(...) keeps rows passing both rules
```{r}
high_quality <- videos %>%
select(video_id, creator_id, impressions_n, watched_n, watch_rate) %>%
filter(watch_rate >= 0.7, impressions_n >= 20)
```

```{r}
nrow(high_quality)
```

```{r}
nrow(videos)
```
# Example 2
What each line does:
• mutate(...) adds a new column without deleting old ones
• rename(...) makes names shorter and easier to read
• arrange(desc(...)) puts largest values at the top
```{r}
video_scores <- videos %>%
mutate(
watched_share = watched_n / impressions_n
) %>%
rename(
impressions = impressions_n,
watched = watched_n
) %>%
arrange(desc(watched_share))
```

# Example 3
Question:
• What are overall totals/averages in the full dataset?
What this returns:
• exactly one row with full-sample metrics
```{r}
videos %>%
summarise(
total_impressions = sum(impressions_n, na.rm = TRUE),
avg_watch_rate = mean(watch_rate, na.rm = TRUE),
n_videos = n()
)
```

# Example 4
Question:
• How do creator-level metrics differ across creators?
What this returns:
• one row per creator_id
```{r}
creator_summary <- videos %>%
group_by(creator_id) %>%
summarise(
videos_n = n(),
impressions_total = sum(impressions_n, na.rm = TRUE),
watch_rate_avg = mean(watch_rate, na.rm = TRUE)
) %>%
arrange(desc(impressions_total))
```

```{r}
n_distinct(videos$creator_id) 
```

```{r}
nrow(creator_summary)
```

# Exercise 2
Create creator_summary from videos with:
1. group_by(creator_id)
2. summarise(videos_n, impressions_total, watch_rate_avg)
3. sorted by impressions_total descending
Then answer in one sentence:
• Which creator has the most impressions?
```{r}
creator_summary <- videos %>%
group_by(creator_id) %>%
summarise(
videos_n = n(),
impressions_total = sum(impressions_n, na.rm = TRUE) ,
watch_rate_avg = mean(watch_rate, na.rm = TRUE)
) %>%
arrange(desc(impressions_total))
```

Question answered: creator 27 has the most impressions (1344)
# Exercise 3
Create object top_watch, that contains the following information: the video id, creator id, watch
rate, and at least 50 impressions per video. Arrange your answer by having watch rate descending.

```{r}
top_watch <- videos %>%
select(video_id, creator_id, watch_rate, impressions_n) %>%
filter(impressions_n >= 50) %>%
arrange(desc(watch_rate))
```

# Exercise 4
Add a new variable and summarize it:
1. create engagement = watched_n / impressions_n using mutate()
2. aggregate by creator_id using group_by() + summarise()
3. compute mean engagement per creator
4. sort descending
Expected output: one row per creator with mean engagement.

```{r}
creator_engagement <- videos %>%
mutate(engagement = watched_n / impressions_n) %>%
group_by(creator_id) %>%
summarise(mean_engagement = mean(engagement, na.rm = TRUE)) %>%
arrange(desc(mean_engagement))

creator_engagement
```